Nail: A practical interface generator for binary formats

### 2014-04-01 paper/intro.tex
another paragraph

A promising approach to avoid such vulnerabilities is to specify
a precise grammar for the input data format, and to use a parser
generator, such as {\tt lex} and {\tt yacc}, to synthesize the input
processing code.  Developers that use a parser generator do not need
to write error-prone input processing code on their own, and as long
as the parser generator is bug-free, the application will be safe from
input processing vulnerabilities.  Unfortunately, applying this approach
in practice, using state-of-the-art parser generators, still requires
too much manual programmer effort, making it error-prone, as we describe
next.

@@

Second, data formats can have constraints XXX todo.
Lengths.
Counts.
Checksums.

Third, applications often need to produce output in the same
format as their input---for example, applications might both
read and write files, or both receive and send network packets.
Most parser generators just focus on parsing an input, rather
than producing an output, thus requiring the programmer to manually
construct outputs, which is error-prone.  Some parser generators, such as
Boost.Spirit~\cite{boost-spirit},
allow reusing the grammar for generating output from the internal
representation.  However, those generators require yet another set of
semantic actions to be written, transforming the internal representation
into an AST\@.

>>>>

A promising approach to avoid such vulnerabilities is to specify
a precise grammar for the input data format, and to use a parser
generator, such as {\tt lex} and {\tt yacc}, to synthesise the input
processing code.  Developers that use a parser generator do not need
to write error-prone input processing code on their own, and as long
as the parser generator is bug-free, the application will be safe from
input processing vulnerabilities.  Unfortunately, applying this approach
in practice, using state-of-the-art parser generators, still requires
too much manual programmer effort, making it error-prone, as we describe
next.

@@

Second,  applications often need to produce output in the same
format as their input---for example, applications might both
read and write files, or both receive and send network packets.
Most parser generators just focus on parsing an input, rather
than producing an output, thus requiring the programmer to manually
construct outputs, which is error-prone.  Some parser generators, such as
Boost.Spirit~\cite{boost-spirit},
allow reusing the grammar for generating output from the internal
representation.  However, those generators require yet another set of
semantic actions to be written, transforming the internal representation
into an AST\@.

Third, data formats can have structural dependencies, such as offset, length and checksum fields
that are hard to express in state-of-the-art grammar languages. Often the programmer is required to
manually write control code, such as re-positioning the parser's input stream, looping over the
invocation of a sub-parser or computing a
checksum over raw input bytes.  Besides leaving much room for errors with offset arithmetic, such
code is usually not reusable when generating output.
